---
title: "MultipleRegress"
author: "Dr K"
date: "November 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```
## make a multiple regression model predicting LENGTH, start with full model using p-value approach   

```{r}
fullup <- lm(LENGTH~ .,data=bears)
summary.lm(fullup)
```
###Take out AGE  

```{r}
MODL7 <- lm(LENGTH~ .-AGE,data=bears)
summary.lm(MODL7)
```
###Now take out NECK  

```{r}
MODL6 <- lm(LENGTH~ .-AGE-NECK,data=bears)
summary.lm(MODL6)
```
###Remove WEIGHT next
```{r}
MODL5 <- lm(LENGTH~ .-AGE-NECK-WEIGHT,data=bears)
summary.lm(MODL5)
```
###Now remove HEADWTH    

```{r}
MODL4 <- lm(LENGTH~ .-AGE-NECK-HEADWTH-WEIGHT,data=bears)
summary.lm(MODL4)
```

```{r}
MODL3 <- lm(LENGTH~ .-AGE-NECK-HEADWTH-WEIGHT-SEX,data=bears)
summary.lm(MODL3)
```

###AdjR^2 Started going from 4 to 3 - so stop at 4



## make a multiple regression model predicting LENGTH, start with full model using Adj$R^2$ approach 



##Model LENGTH ~ .     ("." is shorthand for all variables )

```{r}
fullup <- lm(LENGTH~ .,data=bears)
summary.lm(fullup)
```
```{r}
fullup.1 <- lm(LENGTH~ . -AGE,data=bears)
summary.lm(fullup.1)
```
```{r}
fullup.2<- lm(LENGTH~ .-MONTH,data=bears)
summary.lm(fullup.2)
```

```{r}
fullup.3<- lm(LENGTH~ .-SEX,data=bears)
summary.lm(fullup.3)
```
```{r}
fullup.4 <- lm(LENGTH~ . -HEADLEN,data=bears)
summary.lm(fullup.4)
```
```{r}
fullup.5<- lm(LENGTH~ .-HEADWTH,data=bears)
summary.lm(fullup.5)
```

```{r}
fullup.6<- lm(LENGTH~ .-NECK,data=bears)
summary.lm(fullup.6)
```
```{r}
fullup.7<- lm(LENGTH~ .-CHEST,data=bears)
summary.lm(fullup.7)
```

```{r}
fullup.8<- lm(LENGTH~ .-WEIGHT,data=bears)
summary.lm(fullup.8)
```
  
###At this point we pick the best one, then from there we would take up with that model and one-by-one take out one of the other explanitory variables and select the best of those - and repeat  The one where we took out AGE is best  with Adj$R^2$ .8816

```{r}
fullup.1.2<- lm(LENGTH~ .-AGE-MONTH,data=bears)
summary.lm(fullup.1.2)
```

```{r}
fullup.1.3<- lm(LENGTH~ .-AGE-SEX,data=bears)
summary.lm(fullup.1.3)
```
```{r}
fullup.1.4 <- lm(LENGTH~ . -AGE-HEADLEN,data=bears)
summary.lm(fullup.1.4)
```
```{r}
fullup.1.5<- lm(LENGTH~ .-AGE-HEADWTH,data=bears)
summary.lm(fullup.1.5)
```

```{r}
fullup.1.6<- lm(LENGTH~ .-AGE-NECK,data=bears)
summary.lm(fullup.1.6)
```
```{r}
fullup.1.7<- lm(LENGTH~ .-AGE-CHEST,data=bears)
summary.lm(fullup.1.7)
```

```{r}
fullup.1.8<- lm(LENGTH~ .-AGE-WEIGHT,data=bears)
summary.lm(fullup.1.8)
```
###At this point we pick the best one again, then from there we would take up with that model and one-by-one take out one of the other explanitory variables and select the best of those - and repeat  This time we have a tie between taking out (AGE and HEADLEN) or taking out (AGE and NECK) both have Adj$R^2$ .8839  
  
####This is a pain we must have a better way  
  
#now automate


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(LENGTH ~ .,
               data = bears,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
##Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[4,]
```

```{r}
best.model <- lm(LENGTH~MONTH+SEX+HEADLEN+CHEST,data=bears)
summary(best.model)
```

