---
title: "simpleRegress"
author: "Zaira Gomez"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26

```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).
```{r}
pairs(bears)
```
```{r}
headlen <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(headlen)
summary.lm(headlen)
```
A better variable as apposed to LENGTH  and NECK  we can say that LENGTH  and HEADLEN  illustrate a better variable because it has a larger adjusted R-squared value.The R squared value for LENGTH and NECK was .7476 ,the adjusted R- squared value for LENGTH and HEADLEN was .8434.

