---
title: "Numerical~Numerical template"
author: "Dr K"
date: "November 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# simple regression

This is a template to serve as an example (cut and paste, change variable names)  
we use the ucdavis1 dataset from the tigerstats package.

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
if(!require("rglwidget")) {install.packages("rglwidget");require("rglwidget")}
data(ucdavis1)
davisdata <- na.omit(ucdavis1)
```


###Plot scatterplot

```{r}
plot(Height~dadheight,data=davisdata)
```

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(davisdata,aes(y=Height,x=dadheight))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```
  
  
###get fancy  


```{r}
basicNN + geom_point(aes(col=Sex)) 
```
  
# Numerical results

```{r}
cor(Height~dadheight,data=davisdata)
```

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(Height~dadheight,data=davisdata)
summary.lm(model.1)
```
# now add the model fit to our plot
  
```{r}
basicNN + geom_point(aes(col=Sex)) + geom_smooth(method=lm)
``` 

##Up the game to 2 regressors

```{r}
advNN <- ggplot(davisdata,aes(y=Height,x=dadheight,z=momheight))
```
```{r}
model.2 <- lm(Height~dadheight + momheight,data=davisdata)
summary.lm(model.2)
``` 

##Compare the 2 models note adjR^2 is larger Residual SE is smaller in model.2

```{r}
anova(model.1,model.2)
```

###Test show model.2 better than model.1 (p is low (.0027) so reject $H_0$ )
  
###Code below can be run as a chunk to get interactivity -- so far can't get knitted version to work  
  
```{r}
plot3d(davisdata$Height,davisdata$dadheight,davisdata$momheight)
```
